Toxic Code Snippets on Stack Overflow

### 2018-05-16 cloverflow-tse/cloverflow.tex
Improved the paper based on the responses in the cover letter.

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones''.
There are two directions in creating online code clones: (1)~code is cloned from
a software project to a Q\&A website as an example; or (2)~code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. % and (3)~code is transferred from one
% software project to another via a Q\&A website;
Similar to classic code clones, i.e.~clones between software systems, online
code clones can lead to license violations, bug propagation, introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.

@@

The two toxic code snippets in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times at
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet approximately every 5
days compared to almost every day for the second one. A quick web search shows
that the defective {\small{\texttt{humanReadableInt}}} method in the second
example already appears in approximately 500 projects on GitHub. Considering the
popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippet on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

While research has mostly focused on reusing code snippets \emph{from} Stack
Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), fewer studies have been
conducted on finding the origins of code examples copied \emph{to} Stack
Overflow and the awareness of Stack Overflow developers in doing so. Finding the
origins of code examples reveals the problem of toxic code snippets
caused by outdated code and software licensing violations. It is probably more
important than studying the effects of reusing Stack Overflow code snippets
because it gives insights to the root cause of the problem and lays a
foundation to an automatic technique to detect and report
toxic code snippets on Stack Overflow to developers in the future.

@@

	\item \textbf{Awareness of Stack Overflow answerers and visitors to toxic code
	snippets:} We performed an online survey and collected answers from 201
highly-ranked Stack Overflow users. We found that they cloned code snippets
from open source projects to Stack Overflow answers. While Stack Overflow
answerers are aware of their outdated code snippets, 19\% of the participants
rarely or never fix the code. 99\% of the answerers never include a software
license in their snippets and 69\% never check for licensing conflicts between
the cloned code snippets and Stack Overflow's CC BY-SA 3.0. On the other hand, we also
surveyed 87 Stack Overflow visitors (i.e.~information seekers) on their
experiences to toxic code snippets on Stack Overflow. Sixty-six percent of the
visitors experienced a problem from reusing Stack Overflow code snippets. The
visitors are generally not aware of the CC BY-SA 3.0 license, and more than
half of them never check for license compatibility when reusing Stack Overflow
code snippets.

@@

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016, emse}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. 
The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statements (type-2, type-3). We made sure that they 
detected only non-trivial clones by increasing the minimum clone size to ten
lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

Using the ok-match criterion with a predefined threshold \textit{t} of 0.7
similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC into a single set of 2,289 online
clone pairs. There are only 97 common clone pairs between the two clone sets 
as depicted in~\Cref{fig:clonemerging}.  The low number of common
clone pairs is due to SourcererCC reporting clones with method
boundaries while Simian is purely line-based.

@@

We found that although the answerer have been notified of
outdated code in their answers, for 51.5\% of them such notifications occur very rarely (only 1--20\% of the answers). 
Only 3 participants reported that they were notified in more than 60\% of their answers.

@@

During the manual investigation of 2,289 clone pairs, we identified 226 pairs
as being accidental clones (AC), i.e.~false positives. After removing
them, the set still contains 2,076 true positive clone pairs between 443 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 53.89\%.

@@

\begin{table}
	\centering
	\caption{Statistics of clone sizes}
	\label{tab:clone_stats}
	\begin{tabular}{lrrrr}
		\toprule
		Clones & Min & Max & Mean & Median \\
		\midrule
		QS & 10 & 135 & 18.6 & 14 \\
		SQ & 21 & 21 & 21.0 & 21 \\
		UD & 10 & 104 & 18.1 & 14 \\
		EX & 10 & 48 & 16.7 & 14 \\
		BP & 10 & 55 & 19.9 & 21 \\
		IN & 11 & 22 & 13.8 & 13.0 \\
		\bottomrule
	\end{tabular} 
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{boxplot_clone_size}
	\caption{Size of online code clones.}
	\label{fig:boxplotclonesize}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{boxplot_clone_age}
	\caption{Age of online code clones.}
	\label{fig:boxplotcloneage}
\end{figure}

@@

@@

>>>>

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones''.
There are two directions in creating online code clones: (1)~code is cloned from
a software project to a Q\&A website as an example; or (2)~code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. % and (3)~code is transferred from one
% software project to another via a Q\&A website;
Similar to classic code clones, i.e.~clones between software systems, online
code clones can lead to license violations, bug propagation, introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.
Although this activity of online code cloning is well-known, there is only a few
empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
the on finding the origins of the clones.
We tackle this challenge of establishing existence of online code clones and
investigate how they occur in this study.

@@

The two toxic code snippets in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times\footnote{The number of views
is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).} 
at
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet approximately every 5
days compared to almost every day for the second one. A quick web search shows
that the defective {\small{\texttt{humanReadableInt}}} method in the second
example already appears in approximately 500 projects on GitHub. Considering the
popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippet on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

While research has mostly focused on reusing code snippets \emph{from} Stack
Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), fewer studies have been
conducted on finding the origins of code examples copied \emph{to} Stack
Overflow and the awareness of Stack Overflow developers in doing so. Finding the
origins of code examples reveals the problem of toxic code snippets
caused by outdated code and software licensing violations. It is equally
important to studying the effects of reusing Stack Overflow code snippets
because it gives insights to the root cause of the problem and lays a
foundation to an automatic technique to detect and report
toxic code snippets on Stack Overflow to developers in the future.

@@

	\item \textbf{Awareness of Stack Overflow answerers and visitors to toxic code
	snippets:} We performed an online survey and collected answers from 201
highly-ranked Stack Overflow users and 87 Stack Overflow visitors. 
We found that the answerers cloned code snippets
from open source projects to Stack Overflow answers. While Stack Overflow
answerers are aware of their outdated code snippets, 19\% of the participants
rarely or never fix the code. 99\% of the answerers never include a software
license in their snippets and 69\% never check for licensing conflicts.
On the other hand, 66\% of the
Stack Overflow visitors experienced a problem from reusing Stack Overflow code snippets. 
They are generally not aware of the CC BY-SA 3.0 license, and more than
half of them never check for license compatibility when reusing Stack Overflow
code snippets.

@@

\textbf{Clone Detection Configuration: } We are aware of effects of
configurations to clone detection results and the importance of searching for
optimised configurations in empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016, emse}. However,
considering the massive size of the two datasets and the search space of at
least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
best configurations of the tools. Thus, we decided to configure Simian and
SourcererCC based on their established default configurations chosen by the
tools' creators as depicted in \Cref{tab:clone_config}. 
The two clone detectors complement each
other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
detecting clones with renaming and added/deleted statements (type-2, type-3).

Nevertheless, we have tried varying the minimum clone lines of 6, 10, and larger
than 10 for the two clone detection tools. The minimum clone size of 10 lines is
considered a standard setting for clone detection in large-scale data sets to
avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
setter methods) in the analysis or the manual investigation
phase~\cite{Sajnani2016}. Choosing this size threshold larger than 10 could
possibly remove some non-trivial clones from the analysis, i.e.~create more
false negatives. On the other hand, decreasing the threshold to be lower than 10
lines will result in a larger number of clone candidate pairs to look at and a
higher chance of getting false positives. It is known that lowering the number
of minimum clone lines is harmful to precision. Moreover, the large number of
clone pairs will hinders the full manual validation of the clones and force us
to rely on sampling of clone pairs. We performed an analysis to confirm this. We
started by running the tools with minimum clone size of 10 lines and performing
the manual clone confirmation. Then, we compared the number of true clone pairs
detected if we increase or decrease the size.

\begin{figure}[H] \centering
	\includegraphics[width=0.8\linewidth]{boxplot_clone_size} 
	\caption{Size of online code clones.} 
	\label{fig:boxplotclonesize}
\end{figure}

Regarding increasing the minimum clone size to more than 10 lines (e.g. 15
lines), the result is as shown in
\Cref{fig:boxplotclonesize}. We found that the distribution of true clones; QS,
SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines. Increasing
the threshold to be higher than 10 would remove some of the trivial BP and IN
clone pairs which are not interesting for this study. However, it will also
remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.

Regarding decreasing the minimum clone size to be less than 10 lines, we reran
the two clone detection tools again using a minimum
clone size of 6 lines, another well-accepted minimum clone size in clone
benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
With this large amount of clone
candidate pairs, it is not feasible to manually confirm all of the clones and we
must rely on sampling. This will result in weaker findings and
weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
to keep the balance between the number of non-trivial clone pairs and the
feasibility of manual clone investigation.
%We made sure that they 
%detected only non-trivial clones by increasing the minimum clone size to ten
%lines.
%(denoted as \textit{D}), and (2)~the discovered configurations for
%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
%of optimising clone detectors' configurations based on clone agreement
%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
%In total, we have four configurations: Simian with the default
%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
%NiCad with the default configuration ($N_D$)
%and NiCad with the EvaClone configuration ($N_E$).

@@

The threshold \textit{t} is crucial for the ok-match because it affects the number
of merged clone pairs. Setting a high \textit{t} value will result in a few ok-match clone pairs
and duplicates of the same clone pairs (which are supposed to be merged) may appear in the merged
clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
pairs and some non-duplicate clone pairs may be accidentally merged by only
a few matching lines.
In order to get an optimal $t$ value, we did an analysis by choosing
five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
By setting $t=0.7$ according to Bellon's study, we
found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3,
0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually
checked all the 111 reported pairs. We found one false positive pair and 110
true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false
positive pair and still retained all the 110 true positive pairs. All the clone
pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
subset of $t=0.5$. However, since there is a fewer true positive pairs reported
(i.e.~generating false negatives), we ended up leaving some duplicates of the 
same clones in the final merged clone set.
With this analysis, we can see that setting the threshold $t$ to 0.1 is too
relaxed and results in having false positive ok-match pairs, while setting the
$t$ to 0.7 or 0.9 is too strict and generates some false negative pairs. Thus,
we decided to select the $t$ value at 0.5.

Using the ok-match criterion with the threshold \textit{t} of 0.5
similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC into a single set of 2,289 online
clone pairs. There are only 110 common clone pairs between the two clone sets 
as depicted in~\Cref{fig:clonemerging}.  The low number of common
clone pairs is due to SourcererCC reporting clones with method
boundaries while Simian is purely line-based.

@@

We found that although the answerer have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done by
posting comments for that answer on Stack Overflow. For example, the answerer of
the Stack Overflow question no.~10924648 posted a comment on his own answer
saying that the answer is specifically for Spring 3.1. Moroever, another user
posted a comment on the answer of the post no.~801935 that the code snippet is
not of high quality and suggested an alternative in another post.

@@

Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
as being accidental clones (AC), i.e.~false positives. After removing
them, the set still contains 2,076 true positive clone pairs between 443 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 53.89\%.

@@

%\begin{table}
%	\centering
%	\caption{Statistics of clone sizes}
%	\label{tab:clone_stats}
%	\begin{tabular}{lrrrr}
%		\toprule
%		Clones & Min & Max & Mean & Median \\
%		\midrule
%		QS & 10 & 135 & 18.6 & 14 \\
%		SQ & 21 & 21 & 21.0 & 21 \\
%		UD & 10 & 104 & 18.1 & 14 \\
%		EX & 10 & 48 & 16.7 & 14 \\
%		BP & 10 & 55 & 19.9 & 21 \\
%		IN & 11 & 22 & 13.8 & 13.0 \\
%		\bottomrule
%	\end{tabular} 
%\end{table}

@@

We did an analysis of the time it took for the clone to appear from Qualitas
projects to Stack Overflow. The clone ages were calculated by counting the
number of month difference from the dates of each Qualitas project to the date
the answers were posted on Stack Overflow as shown in~\ref{fig:boxplotcloneage}.
We found that, on average, it took the clones around 2 years since they appeared
in Qualitas projects to appear on Stack Overflow answers. Some of the clones
appeared on Stack Overflow almost at the same time as the original, while the
oldest clones took around 5 years.

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{boxplot_clone_age}
	\caption{Age of QS online code clones.}
	\label{fig:boxplotcloneage}
\end{figure}

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow two years after the snapshot we have (6 May 2018) 
on three aspects: newer or higher-voted answers and comments. We found
that there were 34 posts which contains newer answers. Regarding the number of
votes, there were 5 questions which contained answers with a higher number of
votes than the outdated answer. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, there were 6 answers that had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. None of the 6 answers change their
outdated code, but the comments themselves may help to warn other Stack Overflow
users.

### 2018-05-16 cloverflow-tse/cover_letter/cover_letter.tex
Improved the paper based on the responses in the cover letter.

	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub. However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information. Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
	We also updated the Overall Discussion section to reflect the findings that there is only a few toxic outdated code that are found in open source projects on GitHub. %Moreover, the direction of copying is also unclear. The clones could come from Stack Overflow, the original project repositories, or other places. 
\end{enumerate}

@@

We also updated the Introduction to state that the dominant topic is about online code clones~\FIXME{do it}.
%Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.

@@

That is a fair point and we would like to analyse the statistics as you suggested. Unfortunately, for our experiment, we extracted only the code snippets from the Stack Overflow dumps but not other information. They are the only available data of the January 2016 snapshot we currently have. We checked and found that the latest available Stack Overflow dump already contains different data than the one we used in our study since it is now more than 2 years newer, and will result in incorrect statistics and inconsistent results. Nevertheless, we have modified the text in the Introduction to include your concern ... \FIXME{do it}.

@@

Nevertheless, since this is a very interesting suggestion. We also performed an investigation of the 100 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet. We include the result of this investigation in the RQ regarding outdated code (RQ?). We found that, out of 100 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment). Thus, there is about 6\% of outdated answers that were notified by the Stack Overflow users based on our analysed data. None of the 6 answers change their outdated code, but the comments themselves may help to warn other Stack Overflow users. We added this discussion in the RQ4 \FIXME{do it}.

@@

Fortunately, we could use this opportunity to study the evolution of the toxic code snippets on Stack Overflow. We manually investigated the outdated and license incompatible code snippets that we discovered to see if they are still the same or not. The check was performed on 6 May 2018, approximately 2 years after the snapshot was created. Moreover, we also checked if there is any comment regarding the outdated code or the license of the snippets from other Stack Overflow users. From the 100 outdated answers, we found that four answers were deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue. 
We included this discussion in RQ4 \FIXME{do it}.

@@

That is a fair point. The reason we chose the clone size of at least 10 lines is as follows. The minimum clone size of 10 lines is considered a standard setting for clone detection in large-scale data sets to avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and setter methods) in the analysis or the manual investigation phase~\citep{Sajnani2016}. 
Choosing this size threshold larger than 10 could possibly remove some non-trivial clones from the analysis, i.e.~create more false negatives.
On the other hand, decreasing the threshold to be lower than 10 lines will result in a larger number of clone candidate pairs to look at and a higher chance of getting false positives. Moreover, the large number of clone pairs will hinders the full manual validation of the clones and force us to rely on sampling of clone pairs. We performed a small analysis to confirm this.

@@

Regarding decreasing the minimum clone size to be less than 10 lines, we reran the two clone detection tools (Simian and SourcererCC) again using a minimum clone size of 6 lines, another well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}. Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs using Bellon's ok-match threshold $t=0.5$. With this large amount of clone candidate pairs, it is not feasible to manually confirm all of the clones and we must rely on sampling. This will result in weaker findings and weaker conclusion. Thus, we decide to retain the minimum clone size of 10 lines to keep the balance between the number of non-trivial clone pairs and the feasibility of manual clone investigation.

We have modified the paper to include this discussion in RQ2 \FIXME{do it}.

@@

We selected the Bellon's ok-match threshold of 0.7 because it is a standard value in clone benchmarking \citep{Bellon2007} and also used in other study of clones, e.g.~\cite{Sajnani2016}. Nevertheless, we agree that varying the threshold ($t$) value is beneficial to the validity of the findings so we did an analysis by choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates. As shown in the our paper, by setting $t=0.7$ according to Bellon's study, we found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually checked all the 111 reported pairs.
We found one false positive pair and 110 true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false positive pair and still retained all the 110 true positive pairs. All the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a subset of $t=0.5$. However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates in the final merged clone set.

@@

%Our apologies if the writing in section 3.5.3 confuses you. 
The research question (section 3.5.3) is actually about notifying the answerers that their answers are already outdated, not notifying the users of the outdated code snippets. This notification to the answerer can be done by posting comments for that answer on Stack Overflow. For example, the answerer of the Stack Overflow question no.~10924648 posted a comment on his own answer saying that the answer is specifically for Spring 3.1. Moroever, another user posted a comment on the answer of the post no.~801935 that the code snippet is not of high quality and suggested an alternative in another post. We extended this discussion in RQ4 \FIXME{do it}.

@@

Regarding the age of cloned code on Stack Overflow, we did an analysis of clone ages as you suggested. We only chose the QS clone pairs since we could manually confirmed the direction of cloning. Moreover, we could searched for the date that the cloned version of the QS project appeared, which was not possible for UD, EX, BP, and IN clone pairs. 
We calculated the clone ages by counting the number of month difference from the dates of each Qualitas project to the date the answers were posted on Stack Overflow.
We drew a boxplot as you suggested and included the discussion of the statistics in RQ4. We found that the minimum, maximum, median, and average clone ages were 0, 64, 26.5 and 26 months respectively (also summarised in the table below).

\begin{table}[H]
	\centering
\begin{tabular}{lrrrrr}
	\toprule
	\multirow{2}{*}{Clone pattern} & \multirow{2}{*}{Amount} & \multicolumn{4}{c}{Age of clones (months)} \\ \cmidrule{3-6}
	& & Min & Max & Avg. & Median \\
	\midrule
	QS & 153 & 0 & 64 & 26.5 & 26.0 \\
	\bottomrule
\end{tabular}
\end{table}

>>>>

	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub. However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information. Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
	We also updated the Overall Discussion section to reflect the findings that (1) there is only a small number of toxic code snippets from outdated code that are found in GitHub projects, (2) there is a large number of toxic code snippets from missing license that are found in GitHub projects. %Moreover, the direction of copying is also unclear. The clones could come from Stack Overflow, the original project repositories, or other places. 
\end{enumerate}

@@

We also updated the Introduction to state that the dominant topic is about online code clones as follows.

``Although this activity of online code cloning is well-known, there is only a few
empirical studies on the topic~\citep{An2017,Abdalkareem2017,Baltes2017}, especially
the on finding the origins of the clones.
We tackle this challenge of establishing existence of online code clones and
investigate how they occur in this study.''
%Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.

@@

That is a fair point and we would like to analyse the statistics as you suggested. 
For (a), the number of views
is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).
For (b), unfortunately, for our experiment we extracted only the code snippets from the Stack Overflow dumps but not other information. They are the only available data of the January 2016 snapshot we currently have. We checked and found that the latest available Stack Overflow dump already contains different data than the one we used in our study since it is now more than 2 years newer, and will result in incorrect statistics and inconsistent results.
For (c), that is a really interesting idea. However, it is out of the scope of this study and would involve an extensive analysis of the data so we plan to do it in the future work.

 Nevertheless, we have added a footnote to the text in the Introduction to clarify point (a).

@@

Nevertheless, since this is a very interesting suggestion. We also performed an investigation of the 100 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet. We include the result of this investigation in the RQ4. We found that, out of 100 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment). Thus, there is about 6\% of outdated answers that were notified by the Stack Overflow users based on our analysed data. None of the 6 answers change their outdated code, but the comments themselves may help to warn other Stack Overflow users. We added this discussion in the RQ4.

@@

Fortunately, we could use this opportunity to study the evolution of the toxic code snippets on Stack Overflow. We manually investigated the outdated and license incompatible code snippets that we discovered to see if they are still the same or not. The check was performed on 6 May 2018, approximately 2 years after the snapshot was created. Moreover, we also checked if there is any comment regarding the outdated code or the license of the snippets from other Stack Overflow users. From the 100 outdated answers, we found that four answers were deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue. 
We included this discussion in RQ4.

@@

That is a fair point. The reason we chose the clone size of at least 10 lines is as follows.

The minimum clone size of 10 lines is considered a standard setting for clone detection in large-scale data sets to avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and setter methods) in the analysis or the manual investigation phase~\citep{Sajnani2016}. 
Choosing this size threshold larger than 10 could possibly remove some non-trivial clones from the analysis, i.e.~create more false negatives.
On the other hand, decreasing the threshold to be lower than 10 lines will result in a larger number of clone candidate pairs to look at and a higher chance of getting false positives. Moreover, the large number of clone pairs will hinders the full manual validation of the clones and force us to rely on sampling of clone pairs. We performed a small analysis to confirm this.

@@

Regarding decreasing the minimum clone size to be less than 10 lines, we reran the two clone detection tools (Simian and SourcererCC) again using a minimum clone size of 6 lines, another well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}. Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs using Bellon's ok-match threshold $t=0.5$. With this large amount of clone candidate pairs, it is not feasible to manually confirm all of the clones and we must rely on sampling. Moreover, it is known that lowering the number of minimum clone lines is harmful to precision. This will result in weaker findings and weaker conclusion. Thus, we decide to retain the minimum clone size of 10 lines to keep the balance between the number of non-trivial clone pairs and the feasibility of manual clone investigation.

We have modified the paper to include this discussion in RQ2.

@@

We selected the Bellon's ok-match threshold of 0.7 because it is a standard value in clone benchmarking \citep{Bellon2007} and also used in other study of clones, e.g.~\cite{Sajnani2016}. Nevertheless, we agree that varying the threshold ($t$) value is beneficial to the validity of the findings so we did an analysis by choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates. As shown in the our paper, by setting $t=0.7$ according to Bellon's study, we found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively. an analysis by choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates. As shown in the our paper, by setting $t=0.7$ according to Bellon's study, we found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually checked all the 111 reported pairs.
We found one false positive pair and 110 true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false positive pair and still retained all the 110 true positive pairs. All the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a subset of $t=0.5$. However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates in the final merged clone set.

With this analysis, we can see that setting the threshold $t$ to 0.1 is too relaxed and results in having false positive ok-match pairs, while setting the $t$ to 0.7 or 0.9 is too strict and generates some false negative pairs. Thus, we decided to select the $t$ value at 0.5. This reduces the number of merged clone pairs to 2,290 pairs. All other numbers which derive from this merged clone pairs have been updated accordingly.
Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually checked all the 111 reported pairs.
We found one false positive pair and 110 true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false positive pair and still retained all the 110 true positive pairs. All the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a subset of $t=0.5$. However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates in the final merged clone set.

@@

%Our apologies if the writing in section 3.5.3 confuses you. 
The research question (section 3.5.3) is actually about notifying the answerers that their answers are already outdated, not notifying the users of the outdated code snippets. This notification to the answerer can be done by posting comments for that answer on Stack Overflow. For example, the answerer of the Stack Overflow question no.~10924648 posted a comment on his own answer saying that the answer is specifically for Spring 3.1. Moroever, another user posted a comment on the answer of the post no.~801935 that the code snippet is not of high quality and suggested an alternative in another post. We extended this discussion in Section 3.1.1 (RQ1).

@@

Regarding the age of cloned code on Stack Overflow, we did an analysis of clone ages as you suggested. We only chose the QS clone pairs since we could manually confirmed the direction of cloning. Moreover, we could searched for the date that the cloned version of the QS project appeared, which was not possible for UD, EX, BP, and IN clone pairs. 
We calculated the clone ages by counting the number of month difference from the dates of each Qualitas project to the date the answers were posted on Stack Overflow.
We drew a boxplot as you suggested and included the discussion of the statistics in RQ4. We found that the minimum, maximum, median, and average clone ages were 0, 64, 26.5 and 26 months respectively.  %(also summarised in the table below).

%\begin{table}[H]
%	\centering
%\begin{tabular}{lrrrrr}
%	\toprule
%	\multirow{2}{*}{Clone pattern} & \multirow{2}{*}{Amount} & \multicolumn{4}{c}{Age of clones (months)} \\ \cmidrule{3-6}
%	& & Min & Max & Avg. & Median \\
%	\midrule
%	QS & 153 & 0 & 64 & 26.5 & 26.0 \\
%	\bottomrule
%\end{tabular}
%\end{table}
